AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
poslishes section 3

That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype is starting to tackle few of them. 
Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.

@@

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customisable and accessible tools for a child-centred AIR.

In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, AIR4Children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.

>>>>

That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype, explained in next section, is starting to tackle few of them. 
Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.

@@

\subsection{Open source hardware and software}
Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of 100.00 EUROS. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making affordable, customisable and accessible tools for a child-centred AIR.

That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot \cite{OttoDIY:2016}.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
